UKB Models

### 2023-10-11 ukb_curation-eda.Rmd
updating plot.hist.by.sex() and moving to gamlss_helper_funs.R for easy access across scripts

Look at variances
```{r}
plot.hist.by.sex <- function(data, pheno_list) {

  # Create an empty list to store the ggplot objects
  plots <- list()

  # Loop through the list of variables
  for (pheno in pheno_list) {
    # Check if the variable exists in the data frame
    if (!pheno %in% names(data)) {
      warning(paste("Variable '", pheno, "' not found in the data frame. Skipping..."))
      next
    }

    # Create a ggplot histogram for the variable
    plot <- ggplot(data, aes(x = .data[[pheno]], fill= sex, color=sex)) +
      geom_histogram(alpha=0.5, position="identity") +
      labs(title = paste("Histogram of", pheno), x = pheno, y = "Frequency")

    # Add the plot to the list
    plots[[pheno]] <- plot
  }

  # Return the list of ggplot objects
  return(plots)
}
```

>>>>

Look at variances
